Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-06-25 intro.tex
added more citations

It also complicates matters for tool designers because they might be confronted with text that does not correspond to a well-formed, meaningful program
By analyzing the same data set used in~\cite{6883030}, which contains 1,460 hours of fine-grained code editing logs collected from 21 programmers, we found that 44.2\% of the code edits resulted in syntactically malformed state of the source code.
%\todo{mention YoungSeok's data here}. 
This may be because the programmer is in the midst of a sequence of 
edit actions that leaves the text temporarily malformed or ill-typed, or because the programmer has made a mistake. The language definition is silent about these situations, so it is difficult for tools to help programmers determine and execute a corrective course of action (e.g. by providing \todo{cite study on benefits of syntax highlighting}syntax highlighting and semantics-aware code completion services\todo{cite something?}.)

>>>>

It also complicates matters for tool designers because they might be confronted with text that does not correspond to a well-formed, meaningful program.
By analyzing the same data set used in~\cite{6883030}, which contains 1,460 hours of fine-grained code editing logs collected from 21 programmers, we found that 44.2\% of the code edits resulted in syntactically malformed state of the source code.
%\todo{mention YoungSeok's data here}. 
These malformed states could be errors, but they also may be because the programmer is in the midst of a sequence of edit actions that leaves the text temporarily malformed or ill-typed.
%, or because the programmer has made a mistake. 
The language definition is silent about these situations, so it is difficult for tools to help programmers determine and execute a corrective course of action (e.g. by providing syntax highlighting~\cite{sarkar2015impact} and semantics-aware code completion services~\cite{Mooty:2010:CCC:1915084.1916348}.)
